Dielectric Elastomers (DEs) are a class of Electro Active Polymers (EAPs) that have demonstrated remarkable electrically induced actuation properties \cite{Pelrine_1998,Pelrine_2000,Pelrine_2003,Li_2013_giant_deformation}. These materials are particularly sensitive to changes of the thermal field, but remain frequently unconsidered \cite{Dormann_Odgen_2005,Bustamante_Dorfmann_Ogden_2009,Sansour_2012,Vu_Steinmann_BEM_FEM_3D,Bertoldi_Gei_2011,Gil_electro_partI_2016}. Nonetheless, a thermodynamically consistent framework for the simulation of EAPs under non-isothermal conditions was postulated in Reference \cite{Vertechy2013}. In this connection, numerical studies have been recently published \cite{Hossain_thermo}, where time dependent effects have been restricted to the thermo-visco-elastic behaviour of the material, excluding inertial effects. 


%Energy-Momentum (EM) time integration schemes consistenly reproduce the conservation properties of continua \cite{Betsch_EM_viscoelasticity_2010,Gonzalez_EM_2000,Simo_EM_1992}. 


%Based on this energy (potential) functional, many authors \cite{Betsch2018Thermo,Conde2017} have proposed temperature-based consistent implicit energy momentum (EM) time integration schemes for the long term simulation of structural components governed by this Helmholtz potential. This type of time integration schemes are well-known for their robustness and stability properties due to their structure-preserving features, making them ideal for long term stable simulations. We purposely use the term \emph{temperature-based} to stress the fact that this type of algorithms rely on the temperature field as the thermodynamical state variable and, as such, this temperature represents one of the unknowns to be solved. 

Energy-Momentum (EM) time integration schemes are regarded as both elegant and robust because they are endowed by construction with the discrete analogue of the conservation properties of the continuum, namely the conservation of total energy, linear and angular momenta. The \textit{consistency} of EM schemes refers to their ability to preserve (or dissipate for non-reversible constitutive models) the total energy of a system in agreement with the laws of thermodynamics \cite{Betsch_EM_viscoelasticity_2010,Betsch_EM_mixed_2017,Betsch2018Thermo,Conde2017}. Consistency of these methods is attained by replacing the (exact) partial derivatives of the Helmholtz free energy functional with respect to its arguments ($\vect{C}$ and $\theta$) with their carefully designed algorithmic counterparts. These algorithmic partial derivatives, also known as \textit{discrete derivatives} \cite{Betsch2018Thermo,Betsch_EM_mixed_2017,OrtigosaFranke2018_EM_1,Gonzalez_EM_2000,Simo_EM_1992,Conde2017}, are formulated in compliance with the so-called \textit{directionality property} \cite{Gonzalez_EM_2000}. 





%An alternative approach uses the entropy-based GENERIC framework,
%where the entropy $\eta$ is considered as the thermodynamical state variable (see the works of Romero \cite{Romero2010} and Conde \cite{Conde2017}), where EM schemes have been also successfully developed. However, a well-accepted difficulty of entropy-based formulations is the non-trivial consideration of temperature boundary conditions. Indeed, unless relatively simple thermo-mechanical models are considered, a (computationally expensive) Newton-Raphson type procedure is required in order to solve a nonlinear equation relating $\eta$ and $\theta$ on the part of the boundary subjected to prescribed temperature (at each boundary quadrature point). This is one of the main reasons to prefer the Helmholtz free energy functional as a thermodynamic potential over the internal energy and, thus, the temperature over the entropy as the thermodynamical state variable. 

Very recently, Franke et. al. \cite{Betsch2018Thermo,Betsch_EM_mixed_2017} have proposed a novel EM scheme in the context of nonlinear elasticity and thermo-elasticity, by taking advantage of the concept of polyconvexity \cite{Ball_1976,Ball_1976_2,Ball_2002,Ball_Murat_1976,Schroderbook} and the use of a novel tensor cross product pioneered by de Boer \cite{deBoer_book} and re-discovered in the context of nonlinear continuum mechanics by Bonet et al. \cite{Bonet_cross_product_2016,Bonet_polyconvexity_2015,Bonet_hyperbolicity_partI_2015}. In essence, the authors propose the consideration of four discrete derivatives which are used to form algorithmic versions of the second Piola-Kirchoff stress tensor and the entropy of the system. In addition to the discrete derivative with respect to the temperature, three further discrete derivatives are presented, which represent the algorithmic counterparts of the work conjugates of the right Cauchy-Green deformation tensor, its co-factor and its determinant. This strategy leads to simplified expressions of the algorithmic second Piola-Kirchoff stress tensor and entropy, when comparing against those obtained following the classical approach \cite{Gonzalez_EM_2000}. Furthermore, this work was extended to multiphysics scenarios, such as thermo-elasticity \cite{OrtigosaFranke2020_EM_2}, nonlinear electro-mechanics \cite{OrtigosaFranke2018_EM_1,FrankeOrtigosa2019} and to thermo-electro-mechanics \cite{FrankeOrtigosa2022}.
The aim of the current paper is the development of a new polyconvexity inspired  EM scheme for non-isothermal long-term simulations of DEs, assessing its superiority in terms of long-term stability with respect to other classical time integrators.



%In addition to the broad literature regarding EM time integrators in the context of nonlinear elasticity \cite{Simo_EM_1992,Gonzalez_EM_2000,Betsch_EM_mixed_2017,Betsch_EM_viscoelasticity_2010}, recent works have extended the application of these long-term stable time integrators to multiphysics scenarios, such as thermo-elasticity \cite{Conde2017,Hesch_Betsch_EM_thermo_2011,Betsch2018Thermo,OrtigosaFrankeThermo} and nonlinear electro-mechanics 






The outline of this paper is as follows: in Section \ref{sec:nonlinear continuum electromechanics}, some basic principles of kinematics are presented. 
%The definition of the co-factor and the Jacobian will be based on the tensor cross product operation defined in de Boer \cite{deBoer_book}. 
The governing equations in nonlinear thermo-electro-elastodynamics are also presented in this section. Section \ref{sec:constitutive equations} delves into mathematical requirements inherent to constitutive models in nonlinear thermo-electro-mechanics. 
Section \ref{sec:dynamics} presents the weak forms associated with the governing equations in thermo-electro-elastodynamics. These will help introducing the new temperature-based one-step implicit EM time integrator scheme for thermo-elastodynamics in Section \ref{sec:time integrator}. 
Section \ref{sec:FEM residuals} briefly describes the finite element implementation of the new time integrator scheme and Section \ref{sec:numerical examples} presents a series of numerical examples in order to validate the conservation properties and robustness of the new scheme. 
Finally, Section \ref{sec:conclusions} provides some concluding remarks. 
\ref{sec:entropy-based formulation} presents an entropy-based EM scheme, counterpart of the temperature-based scheme pursued in this paper. \ref{sec:properties directionality} outlines the definition of the discrete derivative expressions featuring in the proposed time integrator in Section \ref{sec:time integrator}. \ref{sec:Betsch formulation} summarises the EM scheme in Reference \cite{Betsch2018Thermo}, illustrating the differences between this and the new EM proposed. \ref{sec:constitutive model appendix} presents  the steps that need to be carried out in order to derive the thermo-elastic constitutive model presented in Section \ref{sec:constitutive models}.


